---
title: "Data Exploaration"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(patchwork)
library(plotly)
library(leaflet)
library(ggplot2)
library(lubridate)

knitr::opts_chunk$set(
  fig.height = 6,
  fig.width = 8,
  message = F,
  echo = T,
  warning = F,
  cache = F
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
cafe = read_csv(here::here("data/Sidewalk_Caf__Licenses_and_Applications_clean.csv"))


parking = read_csv(
  here::here("data/parking_vio2021_cleanv1.csv")) %>% 
  filter(hour != 12.3) %>% 
  filter(hour <= 23) %>% 
  drop_na(address)
```

To get the most comprehesive understanding the distribution of violation tickets
 among NYC, we map all violation to a 3D surface.
 
```{r map,cache=T}
parking %>%
  select(long, lat, hour) %>%
  mutate(long = abs(long)) %>%
  drop_na() %>%
  with(., MASS::kde2d(lat, long)) %>%
  as_tibble() %>%
  plot_ly() %>%
  add_surface(x = ~ x, y = ~ y, z = ~ z) %>%
  layout(scene = list(
    yaixs = list(autorange = "reversed"),
    zaxis = list(
      range = c(0.1, 150),
      title = "",
      showline = FALSE,
      showticklabels = FALSE,
      showline = FALSE,
      showgrid = FALSE
    ),
    camera = list(eye = list(
      x = -1.25, y = 1.25, z = 1.25
    )),
    showlegend = FALSE
  ))
parking %>% 
  drop_na(borough) %>% 
  group_by(borough) %>% 
  summarise(ticket =
              n()/nrow(parking)) %>% 
  arrange(desc(ticket)) %>% 
  pivot_wider(
    names_from = borough,
    values_from = ticket
  ) %>% 
  knitr::kable()
```

\ We can see that most of the violation ticket issued is concentrated in Manhattan by a large margin, followed by Brooklyn at 23.2%. Staten Island has 
the least violation ticket issued.

### Violation counts vs Time

\ Once we have the distribution of the issued tickets, we exploring its characteristics.
Most of the issued ticket of 2020 by the latest data recording is centered at the 3rd quater, this very strange pattern in the normal time wouldn't come to a 
surprise at 2020, as NYC didn't reopen until late May. Once it reopened, the violation 
issued increased exponentially.

```{r bar_by_month}
parking %>% 
  mutate(month = lubridate::month(issue_date),
         month = forcats::fct_reorder(as.factor(month),month)
         ) %>% 
  drop_na(month,borough) %>% 
  group_by(borough,month) %>% 
  summarize(tickets = n()) %>% 
  ungroup() %>%
  mutate(borough = forcats::fct_reorder(borough,tickets,sum)) %>% 
  ggplot(aes(x = month, y = tickets, fill = borough,group = borough)) + 
    geom_bar(stat = "identity",position = "dodge") +
    labs(
      x = 'Issuing Month',
      y = 'counts',
      title = 'The distribution of tickets quantities over month ')
```

\ Trend of violation tickets issued during a day can be seen via the animation below.  As shown, Violation 
tickets mostly issued in the daytime. Two peaks are observed in the animation, 
which is 8 am and 13pm, representing 
`r parking %>% filter(hour==8) %>% nrow()*100/nrow(parking)`% and 
`r parking %>% filter(hour==13) %>% nrow()*100/nrow(parking)`% tickets issued 
of the day.

```{r hour_map,cache=T}
nyc =
  parking %>%
  drop_na(long, lat) %>%
  summarise(
    lon_max = max(long),
    lon_min = min(long),
    lat_max = max(lat),
    lat_min = min(lat)
  )
nyc =
  ggmap::get_map(location = c(
    right = pull(nyc, lon_max),
    left = pull(nyc, lon_min),
    top = pull(nyc, lat_max),
    bottom = pull(nyc, lat_min)
  ))
set.seed(100)
parking %>%
  filter(hour <= 24) %>%
  drop_na(borough,lat,long,hour) %>% 
  sample_n(1e+5) %>% 
  mutate(text_label = str_c("borough:", borough, ",address:", address)) %>% 
  plot_ly()  %>% 
    add_markers(
    y = ~ lat,
    x = ~ long,
    text = ~ text_label,
    alpha = 0.02,
    frame = ~ hour,
    mode = "marker",
    color = ~borough,
    colors = viridis::viridis(4,option = "C")
  ) %>%
  layout(
    images = list(
      source = raster2uri(nyc),
      xref = "x",
      yref = "y",
      y = 40.5,
      x = -74.3	,
      sizey = 0.4,
      sizex = 0.6,
      sizing = "stretch",
      xanchor = "left",
      yanchor = "bottom",
      opacity = 0.4,
      layer = "below"
    )
  )%>%
  animation_opts(transition = 0,frame = 24)
```

\ Group by borough, we seen that these trends vary. As in Manhattan, the peaks 
is similar to the global trend, but other boroughs have a earlier or no second 
peak. This might reflect the nature of most business center is located in Manhattan, and thus has a larger lunch break group.

```{r hour_borough, cache = T}
parking %>% 
  group_by(hour,borough) %>%
  drop_na(hour,borough) %>% 
  summarise(n = n()) %>% 
  plot_ly(x = ~hour, y = ~n, type = 'scatter',mode = 'line', color= ~ borough) %>%
  layout(
    title = 'Violations per Hour',
    xaxis = list(
      type = 'category',
      title = 'Hour',
      range = c(0, 23)),
    yaxis = list(
      title = 'Count of violations'))
```


\ Still, we also intersted in the tickets generated pattern across weekdays.


```{r echo = FALSE, message=FALSE,warning = FALSE}
parking_day = parking %>%
  select(issue_date, summons_number, borough) %>% 
  drop_na(borough)

day_order = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

parking_day %>% 
  mutate(day_week = weekdays(issue_date)) %>%
  group_by(day_week, borough) %>% 
  summarize(n = n()) %>%
  mutate(day_week = factor(day_week, levels = day_order)) %>% 
  arrange(day_week) %>% 
  plot_ly(x = ~ day_week, y = ~ n, type = 'scatter', mode = "line", color = ~borough) %>%
  layout(
    title = 'Violations by weekday',
    xaxis = list(
      type = 'category',
      title = 'Weekday'),
    yaxis = list(
      title = 'Count of violations'))
```

\ According to the figure above, we can see the most obvious pattern is that there are more tickets generated during work days than during weekends . This could be attibuted to two reasons:    

\ 1. the overall demand for parking in NYC are smaller during weekend than during weekdays      

\ 2. Many parking spots are designed to be free parking during weekends.

\ All the five boroughs in NYC--Manhattan, Bronx, Brooklyn, Queens and Staten Island have the same trend in the term of parking tickets generating across a week. Manhattan always has the highest parking tickets volume, and follows with Brooklyn, Queens, Bronx and Staten Island.


### Violation type{.tabset}

\ We want to know the most common reason for getting tickets in NYC, and weather there are differences between the five boroughs.




#### Manhattan
```{r}
vio_code = readxl::read_xlsx('data/ParkingViolationCodes_January2020.xlsx') %>% 
  janitor::clean_names() %>% 
  dplyr::select(violation_code, violation_description) %>% 
  mutate(violation_description = str_to_lower(violation_description))
vio_count_boro = 
  parking %>% 
  left_join(vio_code, by = 'violation_code')
Manhattan_vio = 
  vio_count_boro %>% 
  filter(borough == 'Manhattan') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Manhattan') +
    xlab("violation description") +
    ylab('Count of tickets')  
Queens_vio = 
  vio_count_boro %>% 
  filter(borough == 'Queens') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Queens') +
    xlab("violation description") +
    ylab('Count of tickets') 
Bronx_vio = 
  vio_count_boro %>% 
  filter(borough == 'Bronx') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Bronx') +
    xlab("violation description") +
    ylab('Count of tickets')  
Brooklyn_vio = 
  vio_count_boro %>% 
  filter(borough == 'Brooklyn') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Brooklyn') +
    xlab("violation description") +
    ylab('Count of tickets') 
Staten_vio = 
  vio_count_boro %>% 
  filter(borough == 'Staten Island') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Staten Island') +
    xlab("violation description") +
    ylab('Count of tickets')  
Manhattan_vio
```

#### Queen
```{r}
Queens_vio 
```

#### Bronx
```{r}
Bronx_vio
```

#### Brooklyn
```{r}
Brooklyn_vio
```

#### Staten Island
```{r}
Staten_vio
```



\ Violation types in each borough also have different compositions. Speeding 
through school area is the most common violation in all three borough. No 
standing-day/time limit second common type of violation followed by no 
parking-day/time. No parking street cleaning is the second common type of 
violation in Brooklyn, Queen, Bronx. Fail to display muni meter recept is the 
second most common violation in Stanen Island.

### Fine amount

\ It is also necessary to have a overview of the mean of fined in different boroughs, it might give us rough idea about which area is more risky in the term of getting expensive ticket.



#### Fine amount by boro
```{r}
boro_amount = parking %>% 
  drop_na(fine_amount, borough)%>%
  select(borough, fine_amount)%>%
  group_by(borough) 

boro_amount %>%
  summarize(mean = mean(fine_amount)) %>% 
  knitr::kable()
```

\ The tickets generated in Manhattan are most 'expensive', with the mean of 80.7 dollars. Then followed by Bronx, Staten Island and Brooklyn. The mean of fine amount is lowest in Queens.



```{r}
get_nearby_area =
  function(p_long = 0, p_lat = 0,area=100) {
    return(
      tibble(
        long_lwr = p_long - area / (6378137 * cos(pi * p_lat / 180)) * 180 / pi,
        long_upr = p_long + area / (6378137 * cos(pi * p_lat / 180)) * 180 /
          pi,
        lat_lwr = p_lat - area / 6378137 * 180 / pi,
        lat_upr = p_lat + area / 6378137 * 180 / pi
      )
    )
  }

get_data =
  function(area) {
    data =
      parking %>%
      bind_cols(area) %>%
      filter(long < long_upr,
             long > long_lwr,
             lat < lat_upr,
             lat > lat_lwr) %>% 
  select(summons_number, issue_date, violation_code,hour, vehicle_color, fine_amount)
    
    return(data)
  }

nearby_data = 
  cafe %>%
  select(business_name, business_name2, lat, long, borough)%>%
  mutate(
    nearby = map2(.x = long, .y = lat, ~ get_nearby_area(.x, .y)),
    nearby = map(.x = nearby,  ~ get_data(.x),
    ticket_n = map_dbl(nearby, nrow))) %>% 
  unnest(nearby)
```

#### Risk map (risk is given by rank)



\ Back to the main idea, we still interested in the association between locations of cafes and violations

\ We generate a map in order to show the average fine amount and number of tickets around each cafe, which could provide some information about the parking risk around that cafe. The risk assessment of a cafe is given by the rank of total fine amount around it.

```{r nearby, cache=T}
nearby_data %>% 
  group_by(business_name) %>% 
  summarize(mean_fine = mean(fine_amount),
            n_ticket = n()) %>% 
  left_join(distinct(cafe), by = "business_name") %>% 
  drop_na(mean_fine) %>%
  mutate(percent_rank = rank(-(mean_fine*n_ticket))/908,
         top_risk = ceiling(percent_rank*10)*10) %>% 
  arrange(desc(percent_rank))%>% 
  mutate(pop =
           str_c("<b>",business_name,"</b><br>",
                 "Average fine amount:" ,round(mean_fine, digits = 1),"$","</b><br>",
                 "number of tickets:", n_ticket, "</b><br>",
                 "Risk: top", top_risk, "%","</b><br>")
         ) %>% 
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(
    ~ long,
    ~ lat,
    color = ~ par(mean_fine*n_ticket),
    radius = .1,
    popup = ~ (pop)
  )
```


#### average fine amount distribution
```{r}
nearby_data %>% 
  drop_na(borough) %>% 
  group_by(borough, business_name) %>% 
  summarize(mean_fine = mean(fine_amount)) %>% 
  ggplot(aes(x = mean_fine, fill = borough)) +
  geom_density(alpha = .5)
```

\ From this plot, we could find that the risk of violation to get a cup of coffee is much higher in Brooklyn and Manhattan, you might have to pay 80$ for your parking around cafe in most cases. And in Bronx or Queens, the commonly average fine amount around cafe will reduce to 50. However, we don't get the cafe data in Staten Island, so the situation in Staten Island is unclear.

