---
title: "Data Exploration"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(patchwork)
library(plotly)
library(leaflet)
library(ggplot2)
library(lubridate)

knitr::opts_chunk$set(
  fig.height = 6,
  fig.width = 8,
  message = T,
  echo = T,
  warning = T,
  cache = F
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)

scale_colour_discrete = scale_colour_viridis_d

scale_fill_discrete = scale_fill_viridis_d

```

# Load data
```{r load_data}
cafe = read_csv(here::here("data/Sidewalk_Caf__Licenses_and_Applications_clean.csv"))

parking = read_csv(
  here::here("data/parking_vio2021_cleanv1.csv")) %>% 
  filter(hour != 12.3) 
```

# Cafe Map
```{r cache = F}
plot_cafe_map =
  parking %>%
  count(street_name, name = "ticket") %>%
  right_join(cafe) %>%
  mutate(ticket = replace_na(ticket,1e-10))

pal = colorNumeric(palette = c("viridis", "magma", "inferno","plasma")[[4]],
                   domain = plot_cafe_map$ticket %>% log())

plot_cafe_map =
  plot_cafe_map%>%
  mutate(pop =
           str_c("<b>",business_name,"</b><br>",round(ticket)," tickets")) %>% 
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(
    ~ long,
    ~ lat,
    color = ~pal(ticket %>% log()),
    radius = .1,
    popup = ~ (pop)
  )

plot_cafe_map
```

##Geo vs ticket count
```{r}
parking %>% 
  group_by(borough, lat, long) %>% 
  summarize(tickets_count = n()) %>% 
  mutate(text_label = str_c("Tickets count:", tickets_count, "Borough:", borough)) %>% 
  plot_ly(x = ~lat, y = ~long, z = ~tickets_count, text = ~ text_label) %>%
  add_markers(color = ~tickets_count,
              alpha = 0.0001) 
```


```{r, cache = T}
parking %>%
  dplyr::select(long, lat, hour) %>%
  mutate(long = abs(long)) %>%
  drop_na() %>%
  with(., MASS::kde2d(lat, long)) %>%
  as_tibble() %>%
  plot_ly(x = ~ x, y = ~ y, z = ~ z) %>%
  add_surface() %>%
  layout(scene = list(
    yaixs = list(autorange = "reversed"),
    zaxis = list(
      range = c(1, 150),
      title = "",
      showline = FALSE,
      showticklabels = FALSE,
      showline = FALSE,
      showgrid = FALSE
    ),
    camera = list(eye = list(
      x = -1.25, y = 1.25, z = 1.25
    )),
    showlegend = FALSE
  ))
```


```{r}
parking %>%
  ggplot(aes(x = long, y = lat)) +
  geom_hex() +
  theme(
    legend.position = "right") +
  labs(
    title = "tickets counts show in georaphic information") 
```


## Violation vs Time

1.The distribution of tickets quantities over year

```{r}
parking %>% 
  mutate(month = lubridate::month(issue_date),
         month = forcats::fct_reorder(as.factor(month),month)
         ) %>% 
  drop_na(month,borough) %>% 
  group_by(borough,month) %>% 
  summarize(tickets = n()) %>% 
  ungroup() %>%
  mutate(borough = forcats::fct_reorder(borough,tickets,sum)) %>% 
  ggplot(aes(x = month, y = tickets, fill = borough,group = borough)) + 
    geom_bar(stat = "identity",position = "dodge") +
    labs(
      x = 'Issuing Month',
      y = 'counts',
      title = 'The distribution of tickets quantities over month ')
 
```

Conclusion: This dataset has nearly 39 million observations, most of which are recorded during June, July, August, and September.  


2.plots: violation vs weekday

```{r}
parking_day = parking %>%
  dplyr::select(issue_date, summons_number, borough) %>% 
  drop_na(borough)

day_order = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

parking_day %>% 
  mutate(day_week = weekdays(issue_date)) %>%
  group_by(day_week, borough) %>% 
  summarize(n = n()) %>%
  mutate(day_week = factor(day_week, levels = day_order)) %>% 
  arrange(day_week) %>% 
  plot_ly(x = ~ day_week, y = ~ n, type = 'scatter', mode = "line", color = ~borough) %>%
  layout(
    title = 'Violations by weekday',
    xaxis = list(
      type = 'category',
      title = 'Weekday'),
    yaxis = list(
      title = 'Count of violations'))
```

Conclusion: 
The volume of parking tickets issuing during weekdays are larger than volume of those issuing during weekends. This could be attibuted to two reasons:   
1. the overall demand for parking in NYC are smaller during weekend than during weekdays
2. Many parking spots are designed to be free parking during weekends.

All the five boroughs in NYC--Manhattan, Bronx, Brooklyn, Queens and Staten Island have the same trend in the term of parking tickets generating. Manhattan always has the highest parking tickets volume, and follows with Brooklyn, Queens, Bronx and Staten Island.



3.vilation vs hour
```{r}
parking %>% 
  group_by(hour) %>% 
  summarize(n = n()) %>%
  plot_ly(x = ~hour, y = ~n, type = 'scatter',mode = 'line') %>%
  layout(
    title = 'Violations per Hour',
    xaxis = list(
      type = 'category',
      title = 'Hour',
      range = c(0, 23)),
    yaxis = list(
      title = 'Count of violations'))

parking %>% 
  filter(hour < 23) %>% 
  drop_na(borough) %>% 
  ggplot(aes(x = hour, fill = borough)) +
  geom_bar(stat = "count") +
  labs(title = 'Violations per Hour for each borough') +
  ylab('Count of tickets') +
  scale_x_continuous(breaks=seq(0, 23, 1))
```

During a day, the parking tickets generating has two peaks-- around 8:00 am and aroung 1:00 pm. This may caused by the high parking demand especially during meal time. 



```{r}
vio_code = readxl::read_xlsx('data/ParkingViolationCodes_January2020.xlsx') %>% 
  janitor::clean_names() %>% 
  select(violation_code, violation_description) %>% 
  mutate(violation_description = str_to_lower(violation_description))

vio_count_boro = 
  parking %>% 
  left_join(vio_code, by = 'violation_code')


vio_count_boro %>% 
  group_by(hour,borough) %>% 
  summarise(n = n()) %>% 
  plot_ly(x = ~hour, y = ~n, type = 'scatter',mode = 'line', color= ~ borough) %>%
  layout(
    title = 'Violations per Hour',
    xaxis = list(
      type = 'category',
      title = 'Hour',
      range = c(0, 23)),
    yaxis = list(
      title = 'Count of violations'))
```



##Overall violation type

```{r}
violation_count = 
  parking %>% 
  group_by(violation_code) %>% 
  summarise(n = n()) %>% 
  left_join(vio_code, by = 'violation_code') %>% 
  arrange(desc(n)) %>% 
  filter(n > 10000)
```



bar_plot: 

```{r}
violation_count %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") +
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) 
  
```


The top ten 

##violation type by Borough

```{r}


Manhattan_vio = 
  vio_count_boro %>% 
  filter(borough == 'Manhattan') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Manhattan') +
    xlab("violation description") +
    ylab('Count of tickets')  



Queens_vio = 
  vio_count_boro %>% 
  filter(borough == 'Queens') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Queens') +
    xlab("violation description") +
    ylab('Count of tickets') 


Bronx_vio = 
  vio_count_boro %>% 
  filter(borough == 'Bronx') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Bronx') +
    xlab("violation description") +
    ylab('Count of tickets')  


Brooklyn_vio = 
  vio_count_boro %>% 
  filter(borough == 'Brooklyn') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Brooklyn') +
    xlab("violation description") +
    ylab('Count of tickets') 



Staten_vio = 
  vio_count_boro %>% 
  filter(borough == 'Staten Island') %>% 
  group_by(violation_description) %>% 
  summarize(n = n()) %>% 
  mutate(violation_description = fct_reorder(violation_description, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x = violation_description, y = n, fill = violation_description)) +
  geom_bar(stat = "identity") + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) +
  labs(
    title = 'Top 10 violations in Staten Island') +
    xlab("violation description") +
    ylab('Count of tickets')  


  
Manhattan_vio
Queens_vio 
Bronx_vio
Brooklyn_vio
Staten_vio


```


Anything to do with veihicle_make?

```{r}
parking %>% 
  select(id, vehicle_make) %>% 
  group_by(vehicle_make) %>% 
  summarise(n = n()) %>% 
  filter(n>10) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  mutate(vehicle_make = fct_reorder(vehicle_make, n)) %>% 
  plot_ly(x = ~vehicle_make, y = ~n, type = "bar", colors = "viridis")
```

According to the distribution of vehicle make of the parking ticket dataset, we can roughly know the tops 10 vehicle make that are most popular among new yorkers.

## Some plot/description/test about fine amount
Generate data near by cafe
```{r}
get_nearby_area =
  function(p_long = 0, p_lat = 0,area=100) {
    return(
      tibble(
        long_lwr = p_long - area / (6378137 * cos(pi * p_lat / 180)) * 180 / pi,
        long_upr = p_long + area / (6378137 * cos(pi * p_lat / 180)) * 180 /
          pi,
        lat_lwr = p_lat - area / 6378137 * 180 / pi,
        lat_upr = p_lat + area / 6378137 * 180 / pi
      )
    )
  }

get_data =
  function(area) {
    data =
      parking %>%
      bind_cols(area) %>%
      filter(long < long_upr,
             long > long_lwr,
             lat < lat_upr,
             lat > lat_lwr) %>% 
  select(summons_number, issue_date, violation_code,hour, vehicle_color, fine_amount)
    
    return(data)
  }

nearby_data = 
  cafe %>%
  select(business_name, business_name2, lat, long, borough)%>%
  mutate(
    nearby = map2(.x = long, .y = lat, ~ get_nearby_area(.x, .y)),
    nearby = map(.x = nearby,  ~ get_data(.x),
    ticket_n = map_dbl(nearby, nrow))) %>% 
  unnest(nearby)
```

1. fine amount by boro
```{r}
boro_amount = parking %>% 
  drop_na(fine_amount, borough)%>%
  select(borough, fine_amount)%>%
  group_by(borough) 

boro_amount %>%
  summarize(mean = mean(fine_amount)) %>% 
  knitr::kable()

boro_amount %>%
  ggplot(aes(x = borough, y = fine_amount, fill = borough)) +
  geom_boxplot() +
  ylim(0,200)+
  theme(
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) 
```

2. fine amount near cafe
```{r}
nearby_data %>% 
  group_by(business_name) %>% 
  summarize(mean_fine = mean(fine_amount)) %>% 
  left_join(distinct(cafe), by = "business_name") %>% 
  drop_na(mean_fine) %>%
  mutate(pop =
           str_c("<b>",business_name,"</b><br>","Average fine amount:" ,round(mean_fine, digits = 2),"$")) %>% 
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(
    ~ long,
    ~ lat,
    color = ~pal(mean_fine %>% log()),
    radius = .1,
    popup = ~ (pop)
  )
```



3. fine amount by weekday

```{r}


day_order = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

parking %>%
  dplyr::select(issue_date, fine_amount, borough) %>% 
  drop_na(issue_date) %>% 
  mutate(day_week = weekdays(issue_date),
         day_week = factor(day_week, levels = day_order)) %>% 
  arrange(day_week) %>% 
  ggplot(aes(x = day_week, y = fine_amount, fill = day_week)) +
  geom_boxplot() +
  ylim(0,200) +
  theme(
    legend.position = "right",
    legend.text = element_text(size = 8)
  ) 
```


4. Risk plot






### Initial Design about how to study the correlation of tickets and cafe.

- problem: we have location information(lat, long) for both tickets and cafe. but we cannot define their correlation because they are continuous

- solution: 
-- discrete the NYC district by euqally distribute it into smaller boxes with same area.  
-- consider the cafe and tickets are correlated if their location fall into same box

- some special case:
-- new york is not a square: we simply choose a square big enough to cover the whole new york.
-- if N tickets and M cafe are in the same box: distribute the correlation coefficient averagely.


